### 2023-01-05 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_false_negatives@12603ebc333b15dba0c32d0dd8223a4392f12f8f 🚀

\begin{figure}
\centering
\includegraphics{./figures/uncertainty_sampler.png}
\caption{FIG CAPTION}
\end{figure}

We do this by using the process for simulating a distribution of null
false-negative rates for a given dataset as described above
(fig.~\ref{fig:resampling_concept} (A)). We then consider the output
prediction from an arbitrary prediction model, which is the probability
\(p_{ij}\) that two species \(i\) and \(j\) interact. To get an estimate
of \(p_{ij}\) that accounts for observation error, we resample the
probability of each interaction \(p_{ij}\) by simulating a series of
particles. Each particle is the product of the resampling algorithm
(``Resampling'' within fig.~\ref{fig:resampling:concept} (B)), where the
value of a particle is first drawn from a Bernoulli with weight
\(p_{ij}\), and if that value is true, the value remains true with
probability \(1-p_{fn}\), and if the first draw is false, the value
remains false with probability \(1-p_{fp}\). Over many samples of
particles, the resulting frequency of `true' outcomes is a single
resample of the interaction probability \(p_{ij}^*\). Across many
resamples, this forms a distribution of probabilities which are adjusted
by the true and false negative rates.

@@

In each of these datasets, the joint probability of co-occurrence
\(P(AB)\) is decisively greater than our expectation if species co-occur
in proportion to their relative abundance \(P(A)P(B)\). This suggests
that there may not be as many ``neutrally forbidden links'' (Canard
\emph{et al.} 2012) as we might think, and that the reason we do not
have records of interactions between rare species is probably due to
observation error. This has serious ramifications for the widely
observed property of nestedness seen in bipartite networks (Bascompte \&
Jordano 2007)---perhaps the reason we have lots of observations between
generalists is because they are more abundant, and this is particularly
relevant as we have strong evidence that generalism drives abundance
(Song \emph{et al.} 2022), not vice-versa.

@@

We also should address the impact of false-negatives on the inference of
process and causality in community ecology. We demonstrated that in
model food webs, false-negatives do not impact the measure of total
trophic levels until very high FNR (figure fig.~\ref{fig:addedfnr}(C)),
although we cannot generalize this further to other properties. This has
immediate practical concern for how we design what taxa to sample---does
it matter if the sampled network is fully connected? It has been shown
that the stability of subnetworks can be used to infer the stability of
the metaweb paper beyond a threshold of samples
(\textbf{Song2022RapMon?}). But does this extend to other network
properties? And how can we be sure we are at the threshold at which we
can be confident our sample characterizes the whole system? We suggest
that modeling observation error like we have done here can address these
questions and aid in the design of samples of species interactions. To
try and sample to avoid all false-negatives is a fool's errand. Species
ranges overlap to form mosaics, which themselves are often changing in
time. Communities and networks don't end in space, and the interactions
that connect species on the `periphery' of a given network to species
outside the spatial extent of a given sample will inevitably appear as
false-negatives in practical samples. The goal should instead be to
sample a system enough to have a statistically robust estimate of the
current state and empirical change over time of an ecological community
at a given spatial extent and temporal resolution, and to determine what
the sampling effort required prior to sampling.

@@

\leavevmode\hypertarget{ref-Song2022GenDri}{}%
Song, C., Simmons, B.I., Fortin, M.-J. \& Gonzalez, A. (2022).
Generalism drives abundance: A computational causal discovery approach.
\emph{PLOS Computational Biology}, 18, e1010302.

>>>>

\begin{figure}
\hypertarget{fig:resampling_concept}{%
\centering
\includegraphics{./figures/uncertainty_sampler.png}
\caption{(A) The process for estimating the false-negative rate (FNR)
for an interaction dataset consisting of \(N\) total observed
interactions. (B) The method for resampling interaction probability
based on estimates of false-negative and false-positive rates. (C) The
method for interaction probability resampling applied to three mammals
and three parasites from the Hadfield \emph{et al.} (2014)
dataset.}\label{fig:resampling_concept}
}
\end{figure}

We do this by using the process for simulating a distribution of null
false-negative rates for a given dataset as described above
(fig.~\ref{fig:resampling_concept} (A)). We then consider the output
prediction from an arbitrary prediction model, which is the probability
\(p_{ij}\) that two species \(i\) and \(j\) interact. To get an estimate
of \(p_{ij}\) that accounts for observation error, we resample the
probability of each interaction \(p_{ij}\) by simulating a series of
particles. Each particle is the product of the resampling algorithm
(``Resampling'' within fig.~\ref{fig:resampling_concept} (B)), where the
value of a particle is first drawn from a Bernoulli with weight
\(p_{ij}\), and if that value is true, the value remains true with
probability \(1-p_{fn}\), and if the first draw is false, the value
remains false with probability \(1-p_{fp}\). Over many samples of
particles, the resulting frequency of `true' outcomes is a single
resample of the interaction probability \(p_{ij}^*\). Across many
resamples, this forms a distribution of probabilities which are adjusted
by the true and false negative rates.

@@

In each of these datasets, the joint probability of co-occurrence
\(P(AB)\) is decisively greater than our expectation if species co-occur
in proportion to their relative abundance \(P(A)P(B)\). This suggests
that there may not be as many ``neutrally forbidden links'' (Canard
\emph{et al.} 2012) as we might think, and that the reason we do not
have records of interactions between rare species is probably due to
observation error. This has serious ramifications for the widely
observed property of nestedness seen in bipartite networks (Bascompte \&
Jordano 2007)---perhaps the reason we have lots of observations between
generalists is because they are more abundant, and this is particularly
relevant as we have strong evidence that generalism drives abundance
(Song \emph{et al.} 2022a), not vice-versa.

@@

We also should address the impact of false-negatives on the inference of
process and causality in community ecology. We demonstrated that in
model food webs, false-negatives do not impact the measure of total
trophic levels until very high FNR (figure fig.~\ref{fig:addedfnr}(C)),
although we cannot generalize this further to other properties. This has
immediate practical concern for how we design what taxa to sample---does
it matter if the sampled network is fully connected? It has been shown
that the stability of subnetworks can be used to infer the stability of
the metaweb paper beyond a threshold of samples (Song \emph{et al.}
2022b). But does this extend to other network properties? And how can we
be sure we are at the threshold at which we can be confident our sample
characterizes the whole system? We suggest that modeling observation
error like we have done here can address these questions and aid in the
design of samples of species interactions. To try and sample to avoid
all false-negatives is a fool's errand. Species ranges overlap to form
mosaics, which themselves are often changing in time. Communities and
networks don't end in space, and the interactions that connect species
on the `periphery' of a given network to species outside the spatial
extent of a given sample will inevitably appear as false-negatives in
practical samples. The goal should instead be to sample a system enough
to have a statistically robust estimate of the current state and
empirical change over time of an ecological community at a given spatial
extent and temporal resolution, and to determine what the sampling
effort required prior to sampling.

@@

\leavevmode\hypertarget{ref-Song2022GenDri}{}%
Song, C., Simmons, B.I., Fortin, M.-J. \& Gonzalez, A. (2022a).
Generalism drives abundance: A computational causal discovery approach.
\emph{PLOS Computational Biology}, 18, e1010302.

\leavevmode\hypertarget{ref-Song2022RapMon}{}%
Song, C., Simmons, B.I., Fortin, M.-J., Gonzalez, A., Kaiser-Bunbury,
C.N. \& Saavedra, S. (2022b). Rapid monitoring for ecological
persistence.
